Universal Anonymous Signatures

### 2022-05-05 prism-backend/research/gsac/sec-gsac.tex
Making a pass.

\todo{I think we should extend ``vanilla'' \GSAC to return the full \Attrs
  in \Open, but without needing \trans as a parameter to \Open (for compatibility
  with \UAS). This can be done by encrypting all attributes, including their
  ciphertext in the signature, and proving they are part of the credential. This
  would render the scheme too costly, but helps in arguing in favour of \UAS.
  Still, leaving that for after having updated the \UAS section, to see how
  it fits the global picture.}

>>>>

\todo{I think we should extend ``vanilla'' \GSAC to return the full \attrs
  in \Open, but without needing \trans as a parameter to \Open (for compatibility
  with \UAS). This can be done by encrypting all attributes, including their
  ciphertext in the signature, and proving they are part of the credential. This
  would render the scheme too costly, but helps in arguing in favour of \UAS.
  Still, leaving that for after having updated the \UAS section, to see how
  it fits the global picture.}

### 2022-05-05 prism-backend/research/gsac/sec-uas.tex
Making a pass.

\GSAC is a very interesting exercise that showcases the advantages of direct
combination of group signatures and anonymous credentials. However, it also
inherits a main limitation: it is too strict in regards to the utility it
offers. The most excruciating example of this fact is that in \GSAC, via \Open,
one can only get the actual identity of the signer. Even though with the inclusion
of attributes the concept of ``identity'' can now be meaningfully defined, we
may not want to fully de-anonymize the signer. Instead, we may be interested in
revealing arbitrary functions of its identity and the signed message. Also, for
the sake of illustation, we restricted to the case of selective disclosure, and
to only one credential per signature. Then, the natural question is whether we
can model an extension to \GSAC that is compatible both with constructions with
that support selective disclosure, and with constructions that support arbitrary
claims on the
credential attributes; and, as it is also common in the anonymous credentials
(or verifiable credentials \needcite) domains, to allow credential holders to
combine multiple credentials into one signature/presentation. Similarly, we can
also generalize \GSAC by allowing users to leverage previously obtained
credentials in order to obtain new ones; possibly, applying arbitrary issuance
policies. In a nutshell, our generalization of \GSAC into Universal Anonymous
Signatures (\UAS), enables:

\begin{itemize}
\item Using previously obtained credentials to request new ones, applying
  arbitrary policies to the credentials involved in the request, in
  order to determine whether the new issuance should proceed or not.
\item Modulating the type of utility one wants to get directly from signatures.
  That is, let signatures disclose a subset of the attributes in the credentials
  involved in the signing process, prove arbitrary claims over those attributes,
  or even reveal absolutely nothing at all beyond that that an owner of a valid
  credential created the signature.
\item Defining arbitrary de-anonymization functions, over the signer's
  credentials and signed message. This can range from producing the user public
  key (as in group signatures), to disallowing any kind of de-anonymization,
  passing through any intermediate de-anonymization function, like revealing
  the nationality of the signer, or its banking account number, even if this
  was not revealed at the signing stage.
\end{itemize}

>>>>

\GSAC is a very interesting exercise that showcases the advantages of direct
combination of group signatures and anonymous credentials. However, it also
inherits a main limitation: it is too strict in regards to the utility it
offers. The most excruciating example of this fact is that in \GSAC, via \Open,
one can only get the actual identity of the signer. Even though the inclusion
of attributes makes the concept of ``identity'' meaningful, we
may not want to fully de-anonymize the signer. Instead, we may be interested in
revealing arbitrary functions of its identity and the signed message. Also, for
the sake of illustation, we restricted to the case of selective disclosure, and
to only one credential per signature. Then, the natural question is whether we
can model an extension to \GSAC that is compatible both with constructions with
that support selective disclosure, and with constructions that support arbitrary
claims on the
credential attributes; and, as it is also common in the anonymous credentials
(or verifiable credentials\footnote{\url{https://www.w3.org/TR/vc-data-model/}.
  Last access, May 5th, 2022.}) domains, to allow credential holders to
combine multiple credentials into one signature/presentation. Similarly, we can
also generalize \GSAC by allowing users to leverage previously obtained
credentials in order to obtain new ones; possibly, applying arbitrary issuance
policies. In a nutshell, our generalization of \GSAC into Universal Anonymous
Signatures (\UAS), enables:

\begin{itemize}
\item Using previously obtained credentials to request new ones, applying
  arbitrary policies to the credentials involved in the request, in
  order to determine whether the new issuance should proceed or not.
\item Modulating the type of utility one wants to get directly from signatures.
  That is, let signatures disclose a subset of the attributes in the credentials
  involved in the signing process, prove arbitrary claims over those attributes,
  or even reveal absolutely nothing at all beyond that that an owner of a valid
  credential created the signature.
\item Defining arbitrary de-anonymization functions, over the signer's
  credentials and signed message. This can range from producing the user public
  key (as in group signatures), to disallowing any kind of de-anonymization,
  passing through any intermediate de-anonymization function, like revealing
  concrete attributes, or functions of them.
\end{itemize}
